```{r data generation, echo = FALSE, results = "hide", message=F, warning=F}
library(exams)
library(tidyverse)
library(gt)
library(showtext)
library(xaringanExtra)

font_add_google(name = "Caveat", family = "Caveat")
showtext_auto()
stock_soln <- 50
std_conc <- c(2, 4, 6, 8)
total_vol <- rep(20, length(std_conc))
stock_vol <- std_conc*total_vol / stock_soln
water_vol <- total_vol - stock_vol


sol <- c(stock_vol, water_vol)
lab <- c("Standard Conc. (ppm)", 
         "Volume Stock Added (mL)", 
         "Volume deionised water added (mL)", 
         "Total volume (mL)")
stock_numbers <- 1:4
stock_answers <- glue::glue("##ANSWER{stock_numbers}##")
water_numbers <- 5:8
water_answers <- glue::glue("##ANSWER{water_numbers}##")

my_table <- tibble(std_conc, stock_answers, water_answers, total_vol)
```


Question
========

```{r embed-xaringan, echo=FALSE}
xaringanExtra::embed_xaringan(url = "https://leaflet-extras.github.io/leaflet-map/demo.html", ratio = "16:9")
```


Calculate the amount of stock solution and de-ionised water required to make up the following solutions. The concentration of the stock solution is `r stock_soln` ppm.
How much of the stock standard to add to a certain volume flask. I put units in the top row so answers are numbers only. Stock solution is eg 50ppm.  


```{r echo = F}
my_table %>% 
  gt() %>% 
  cols_label(std_conc = "Standard Conc. (ppm)",
             stock_answers = "Volume Stock Added (mL)", 
             water_answers ="Volume deionised water added (mL)", 
             total_vol = "Total volume (mL)") %>% 
  cols_align(align = "center") %>% 
  tab_options(column_labels.background.color = "cornflowerblue", 
              table.font.names = "Caveat",
              table.font.style = "oblique",
              column_labels.font.weight = "bold",
              column_labels.vlines.width = 1,
              column_labels.vlines.color = "darkblue",
              column_labels.vlines.style = "solid",
              table_body.vlines.width = 1,
              table_body.vlines.color = "darkblue",
              table_body.vlines.style = "solid"
              )
```


<!-- |$Standard\\Concentration\:(ppm)$|$Volume\:of\\Stock\:Added\:(mL)$|$Volume\:deionised\\Water\:Added\: (mL)$|$Total\\Volume\:(mL)$| -->
<!-- |:---------------:|:------------------:|:----------------:|:--------------------:| -->
<!-- | `r std_conc[1]` | \#\#ANSWER1\#\# | \#\#ANSWER5\#\# |  `r total_vol[1]`  | -->
<!-- | `r std_conc[2]` | \#\#ANSWER2\#\# | \#\#ANSWER6\#\# |  `r total_vol[2]`  | -->
<!-- | `r std_conc[3]` | \#\#ANSWER3\#\# | \#\#ANSWER7\#\# |  `r total_vol[3]`  | -->
<!-- | `r std_conc[4]` | \#\#ANSWER4\#\# | \#\#ANSWER8\#\# |  `r total_vol[4]`  |  -->

```{r questionlist, echo = FALSE, results = "asis"}
answerlist(rep("", length(sol)), markup = "markdown")
```


Solution
========

Using the information from the text, we can directly calculate the following joint probabilities:

```{r solutionlist, echo = FALSE, results = "asis"}
answerlist(c(glue::glue("{stock_vol} {lab[2]}"), glue::glue("{water_vol} {lab[3]}")), markup = "markdown")
```


Meta-information
================
extype: cloze
exsolution: `r paste(sol, collapse = "|")`
exclozetype: num|num|num|num|num|num|num|num
exname: stocks
extol: 0.05
exextra[numwidth,logical]: TRUE