```{r data generation, echo = FALSE, results = "hide", message=F, warning=F}
library(exams)
library(tidyverse)
library(palmerpenguins)

my_diamonds1 <- penguins |> 
  select(where(is.numeric))
parameters <- names(my_diamonds1)
index <- sample(1:length(parameters), 1)
function_index <- sample(1:6, 1)

my_diamonds <- my_diamonds1 |> pull(parameters[index])
my_functions <- c("mean", "max", "min", "median", "sd", "range")

solution <- case_when(
  function_index == 1 ~ mean(my_diamonds, na.rm = T),
  function_index == 2 ~ max(my_diamonds, na.rm = T),
  function_index == 3 ~ min(my_diamonds, na.rm = T),
  function_index == 4 ~ median(my_diamonds, na.rm = T),
  function_index == 5 ~ sd(my_diamonds, na.rm = T),
  function_index == 6 ~ max(my_diamonds, na.rm = T)-min(my_diamonds, na.rm = T)
) |> signif(3)


```


Question
========
Below is an excerpt from the penguins dataset of the `palmerpenguins` package (if not already installed, use `install.packages("palmerpenguins")`):

```{r}
library(tidyverse)
library(palmerpenguins)
head(penguins)
```

Calculate the `r my_functions[function_index]` for the `r parameters[index]` of this dataset.


Solution
========
Use the R command `r my_functions[function_index]`(penguins$`r parameters[index]`)



Meta-information
================
extype: num
exsolution: `r solution %>% signif(3)`
exname: penguinstats
extol: `r solution*0.05`
