```{r data generation, echo = FALSE, results = "hide", message=F, warning=F}
library(exams)
library(tidyverse)

gene_data <- read_rds("https://github.com/eugene100hickey/ATU-2023/blob/main/rexams/data/ABA-adult?raw=true")
brain_data <- read_rds("https://github.com/eugene100hickey/ATU-2023/blob/main/rexams/data/brain-area-code?raw=true")
my_brain_area <- brain_data$brain_area |> sample(1)

z1 <- gene_data |> 
  left_join(brain_data)

z2 <- z1 |> 
  filter(brain_area == my_brain_area)

solution <- mean(z2$signal) |> signif(3)
```


Question
========
Run the code lines below to read in two data frames called `gene_data` and `brain_data`. 

```{r eval=FALSE}
gene_data <- read_rds("https://github.com/eugene100hickey/ATU-2023/blob/main/rexams/data/ABA-adult?raw=true")
brain_data <- read_rds("https://github.com/eugene100hickey/ATU-2023/blob/main/rexams/data/brain-area-code?raw=true")
```

Then join these two data frames together to make one where the first few rows look like this:

```{r echo=FALSE}
gt::gt(z1 |> head())
```

`hgnc_xsymbol` refers to the name of the gene, `structure` is a code number for the specific brain area, `signal` measures how active the gene is in this brain area, and `brain_area` is the name for  the general brain area.

Filter this to only look at gene expression from the `r my_brain_area`. 

What is the average gene expression in `r my_brain_area`?



Solution
========
Use `gene_data |> left_join(brain_data, join_by(structure == brain_code))` and then `filter(brain_area == `r my_brain_area`)`



Meta-information
================
extype: num
exsolution: `r solution`
exname: ABAData-join
extol: `r solution*0.002`
