```{r data generation, echo = FALSE, results = "hide", message=F, warning=F}
library(exams)
library(tidyverse)
library(dslabs)

my_number <- sample(1:100, 1)
set.seed(my_number)
z <- rfalling_object(n = 1000) |> 
  mutate(inaccuracy = abs(distance - observed_distance))

solution <- sum(z$inaccuracy) |> round(0)

```


Question
========
Install the `dslabs` package if you haven't already (`install.packages("dslabs")`). Create an `rfalling_object` using the code below (note, the `set.seed()` is crucial otherwise the random number generator won't be the same. Use the value `r my_number` for `my_number`)

```{r eval=FALSE}
library(tidyverse)
library(dslabs)

set.seed(my_number)
falling <- rfalling_object(n = 1000)
```

Create a new column using `mutate()` of the absolute value difference between the `distance` and `observed_distance` columns (the R function `abs()` will be useful). What is the sum of the values in this column? Give your answer to the nearest whole number.

Solution
========
Use `mutate(inaccuracy = abs(distance - observed_distance))`.



Meta-information
================
extype: num
exsolution: `r solution %>% signif(4)`
exname: us-contagious
extol: `r solution*0.002`
