```{r data generation, echo = FALSE, results = "hide", message=F, warning=F}
library(exams)
library(tidyverse)

state_areas <- read_rds("https://github.com/eugene100hickey/ATU-2023/blob/main/rexams/data/state-areas?raw=true")
state_regions <- read_rds("https://github.com/eugene100hickey/ATU-2023/blob/main/rexams/data/state-regions?raw=true")

states <- state_regions |> 
  left_join(state_areas, join_by(state == state_name))
regions <- levels(states$region)
my_region <- sample(regions, 1)
solution <- states |> 
  filter(region == my_region) |> 
  pull(area) |> 
  sum(na.rm = T) |> 
  signif(3)
```


Question
========
Run the code lines below to read in two data frames called `state_areas` and `state_regions`. 

```{r eval=FALSE}
state_areas <- read_rds("https://github.com/eugene100hickey/ATU-2023/blob/main/rexams/data/state-areas?raw=true")
state_regions <- read_rds("https://github.com/eugene100hickey/ATU-2023/blob/main/rexams/data/state-regions?raw=true")
```

Then join these two data frames together to make one that looks like this:

```{r echo=FALSE}
gt::gt(states |> head())
```

What is the sum of the area of the states in the `r my_region`?

Solution
========
Use `left_join(state_areas, join_by(state == state_name))`.



Meta-information
================
extype: num
exsolution: `r solution`
exname: us-areas-join
extol: `r solution*0.02`
