```{r data generation, echo = FALSE, results = "hide", message=F, warning=F}
library(exams)
library(tidyverse)
library(dslabs)

repeat{
  my_year <- unique(dslabs::us_contagious_diseases$year) |> 
    sample(1)
  my_disease <- levels(dslabs::us_contagious_diseases$disease) |> 
    sample(1)
  
  z <- dslabs::us_contagious_diseases |> 
    select(disease, state, year, count) |> 
    filter(year == my_year,
           disease == my_disease)
  
  solution <- sum(z$count, na.rm = T) %>% signif(3)
  
  if(!is.na(solution) & solution > 0 ){
    break
  }
}
```


Question
========
Below is an excerpt from the `us_contagious_diseases` dataset of the `dslabs` package (if not already installed, use `install.packages("dslabs")`):

```{r}
library(tidyverse)
library(dslabs)
head(us_contagious_diseases)
```

Calculate the total number of cases in the entire US of `r my_disease` in the year `r my_year`.


Solution
========
Filter for the year and disease using us_contagious_disease |> filter(year == "`r my_year`", disease == "`r my_disease`") and then sum the `count` column.



Meta-information
================
extype: num
exsolution: `r solution`
exname: us-contagious
extol: `r solution*0.05`
