```{r data generation, echo = FALSE, results = "hide", message=F, warning=F}
library(exams)
library(tidyverse)
library(gt)

my_month <- 5:9 |> 
  sample(1)
month_name <- month.name[my_month]
my_variable <- tribble(~dataset_name, ~variable_name,
                      "Temp", "Temperature in Fahrenheit",
                      "Wind", "Wind Speed in mph")
variable_index <- 1:2 |> sample(1)
my_variable <- my_variable[variable_index,]

my_data <- airquality |> 
  filter(Month == my_month)
n <- nrow(my_data)
s <- ifelse(my_variable$dataset_name == "Temp", sd(my_data$Temp), sd(my_data$Wind))
xbar <- ifelse(my_variable$dataset_name == "Temp", mean(my_data$Temp), mean(my_data$Wind))

margin <- qt(0.975, df=n-1)*s/sqrt(n)

conf_int <- (xbar + c(-margin, +margin)) |> 
  signif(4)

water_numbers <- 1:2
conf_int_answer <- glue::glue("##ANSWER{water_numbers}##")

my_table <- tibble(interval = c("Lower Interval", "Higher Interval"), conf_int_answer)
```


Question
========
Load up the `tidyverse` package, and examine the `airquality` dataset therein. This contains daily air quality measurements in New York, May to September 1973. For the month of __`r month_name`__, calculate the 95% confidence interval for the _`mean`_ of the __`r my_variable$variable_name`__ using a _t test_. 


```{r echo = F}
my_table %>% 
  gt() %>% 
  cols_label(interval = "95% Bounds",
             conf_int_answer = "Confidence Interval for Mean") %>% 
  cols_align(align = "center") %>% 
  tab_options(column_labels.background.color = "cornflowerblue", 
              table.font.names = "Caveat",
              table.font.style = "oblique",
              column_labels.font.weight = "bold",
              column_labels.vlines.width = 1,
              column_labels.vlines.color = "darkblue",
              column_labels.vlines.style = "solid",
              table_body.vlines.width = 1,
              table_body.vlines.color = "darkblue",
              table_body.vlines.style = "solid"
              )
```


Solution
========
Use `margin <- qt(0.975, df=n-1)*s/sqrt(n)`, then `xbar + c(-margin, +margin)` where `xbar` is the mean, `n` is the number of samples,and `s` is the sample standard deviation.



Meta-information
================
extype: cloze
exsolution: `r paste(conf_int, collapse = "|")`
exclozetype: num|num
exname: conf_int
extol: 0.05
exextra[numwidth,logical]: TRUE
