```{r data generation, echo = FALSE, results = "hide", message=F, warning=F}
library(exams)
library(tidyverse)
library(gt)
library(agridat)

my_year <- 1970:1971 |> 
  sample(1)

my_loc <- table(australia.soybean$loc) |> 
  names() |> 
  sample(1)

quant <- 5:10 |> 
  sample(1)

my_data <- australia.soybean |> 
  filter(year == my_year, loc == my_loc)
my_quant <- names(my_data)[quant]
my_variable <- my_data[,quant]
conf_int <- t.test(my_variable)$`conf.int` |> signif(3)

water_numbers <- 1:2
conf_int_answer <- glue::glue("##ANSWER{water_numbers}##")

my_table <- tibble(interval = c("Lower Interval", "Higher Interval"), conf_int_answer)
```


Question
========
<font size="+10">Install the `agridat` package from _CRAN_ (use `install.packages("agridat")`). Load up the `australia.soybean` data therein. 

This contains yield and other traits of 58 varieties of soybeans, grown in four locations across two years in Australia.  

For the year __`r my_year`__ and location __`r my_loc`__, calculate the 95% confidence interval for the _`mean`_ of __`r my_quant`__ using a _t test_. </font>


```{r echo = F}
my_table %>% 
  gt() %>% 
  cols_label(interval = "95% Bounds",
             conf_int_answer = "Confidence Interval for Mean") %>% 
  cols_align(align = "center") %>% 
  tab_options(column_labels.background.color = "cornflowerblue", 
              table.font.names = "Caveat",
              table.font.style = "oblique",
              table.font.size = 40,
              column_labels.font.weight = "bold",
              column_labels.vlines.width = 1,
              column_labels.vlines.color = "darkblue",
              column_labels.vlines.style = "solid",
              table_body.vlines.width = 1,
              table_body.vlines.color = "darkblue",
              table_body.vlines.style = "solid"
              )
```


Solution
========
Use `australia.soybean |> filter(year == `r my_year`, loc == `r my_loc`)` and then `t.test()`



Meta-information
================
extype: cloze
exsolution: `r paste(conf_int, collapse = "|")`
exclozetype: num|num
exname: conf_int
extol: 0.05
exextra[numwidth,logical]: TRUE
