---
title: "Colours (and facets)"
author: "Eugene"
date: "`r format(Sys.Date(), '%B %d %Y')`"
output:
  xaringan::moon_reader:
    css: [TUD01, TUD02, tamu-fonts]

header-includes:
- \usepackage{multicol}
- \newcommand{\btwocol}{\begin{multicols}{2}}
- \newcommand{\etwocol}{\end{multicols}}
---

class: center, inverse

# Choice of Colours in R
<br>

### We'll also discuss faceting.
<br>
<br>
- colours are very important
    - second only to position for perception
- can carry information
- also important to be visually pleasing
- worthwhile to make your figures aesthetically attractive
    - visualisations that are engaging are more effective

---
### Types of Colour Scales

- qualitative
    - suite of colours that are easily distinguished
    - no heirarchy
    - caters for visual impairments

```{r qualitative_palette, echo = F, message = F, warning=F, fig.height=4}
library(tidyverse)
library(RColorBrewer)
library(dslabs)
library(MASS)
display.brewer.pal(8, name = "Accent")
```

---


- sequential
    - band of colours that are increasingly intense
    - go from low to high
    
    
```{r sequential_palette, echo = F, message = F, warning=F, fig.height=4}
display.brewer.pal(8, name = "BuGn")
```

---

- diverging
    - suite of colours that go from minus to plus
    - contrasting colours at each end
    - something bland and neutral in the middle

    
```{r diverging_palette, echo = F, message = F, warning=F, fig.height=4}
display.brewer.pal(8, name = "PRGn")
```
---

# Getting Colours in R

- some really great packages
    - RColorBrewer()
        - excellent package giving fine control over palette choice
    - viridis()
        - excels at palettes for vision-impaired readers
    - paletteer()
        - collection of palettes from various sources
    - wesanderson
        - *names(wes_palettes)* followed by *wes_palette("BottleRocket1")*

---

- more....
    - tvthemes()
        - not just colours, but layouts and fonts
        - everything from Game of Thrones to Spongebob (yes, really)
    - ggsci(), palettes for scientific publications (Lancet, AAAS, etc)
    - colorspace()
        - resources for picking colours
        - choose_color() and choose_palette()
        - can convert colours based on vision deficiencies
        - will convert from colour descriptions, e.g. hex2RGB()
- and a [cheatsheet](https://www.nceas.ucsb.edu/~frazier/RSpatialGuides/colorPaletteCheatsheet.pdf)

---

## Ways of Describing Colours

- by name: "red", "cyan", "violetred4", "thistle".....
    - get full list of 657 available in R from _colors()_
- by hex code: "#f49340", "#40f9f9", "#ee82ef", "#d8bfd1"....
- by rgb values: (249, 67, 64), (64, 249, 249), (57, 14, 30), (216, 191, 209)....
- by hcl values: (53.24, 179.04, 12.17), (91.11, 72.10, 192.17), (32.36, 63.11, 349.86), (80.08, 20.79, 307.73)....

---

# Investigating Colours in R

- the following code shows the first "N" colours in R where N is set to 20 here:

```{r base_colours, message = F, warning = F, fig.height=3}
N <- 20
data.frame(col = colors()[1:N]) %>% 
  ggplot(aes(x = col, fill = col)) + 
  geom_bar(position = "stack", show.legend = F) + 
  coord_flip() + 
  theme_minimal() + 
  theme(axis.text.x = element_blank(), axis.title.x = element_blank(), axis.text.y = element_blank())
```

---

## Other Usful Functions

- _show_col()_ from the _scales_ package is super useful
    - e.g. show_col("red") or show_col("#84a412")
- *rgb()* will give a hex code for a fraction of red, green, blue
    - e.g. rgb(0.4, 0.2, 0.5) gives "#663380"
- *colourPicker()* from the colourpicker package
    - colourPicker(numCols = 4), opens up shiny app, returns colours
- *col2rgb()*, also *col2hex()* from the _gplots_ package, and *col2hcl* from the _jmw86069/jamba_ package
    - this last is on github, so you must install the package _devtools_ then do _install_github( jmw86069/jamba)_

---

# Some Websites and Tools

- [coolors.co](coolors.co)
    - will generate appropriate palettes
- [colorpicker](http://tristen.ca/hcl-picker/#/hlc/6/1.1/8C4443/845128)
- [colorspace](http://colorspace.r-forge.r-project.org/articles/hcl_palettes.html#qualitative-palettes)
- Chrome has an _**Eye Dropper**_ tool
    - click on part of a webpage and it will tell you the colour
- Nice description of colurs from [Stowers](https://www.uv.es/conesa/CursoR/material/UsingColorInR.pdf)
    
---

# Colours in _ggplot()_

- use for _fill_ and for _col_ aesthetics
- add the _scale_fill_... and _scale_color_... layers to control
- explore these by typing _?scale_fill_ and then TAB to see the range of options

---

class: center, inverse

# _faceting_

- Faceting means producing multiple panels of a plot
- Splits a plot into several versions based on a categorical variable
- functions _facet_wrap()_ and _facet_grid()_
- useful when lots of data in different subsets
- important to keep axis scales the same

---

```{r facet_example1, echo = T, message=F, warning=F, fig.height=5, fig.width=12}
sex <- c("Female", "Male")
names(sex) <- c("F", "M")
cats %>%     ### cats dataset from MASS
  ggplot(aes(Bwt, Hwt)) + 
  geom_point() + 
  geom_smooth(aes(col = Sex), show.legend = F, se = F) + 
  facet_grid(~Sex, labeller = labeller(Sex = sex)) + 
  labs(x = "Bodyweight (kg)", y = "Heart Weight (g)") +
  theme_minimal() + 
  theme(strip.background = element_blank(), text = element_text(size = 20))
```

---

```{r facet_example2, message = F, warning = F, fig.height=6, fig.width=12}
movielens %>%      ### movielens dataset from dslabs
  mutate(genres = str_replace(genres, pattern = "\\|.*", "")) %>% 
  filter(genres != "(no genres listed)") %>% 
  ggplot(aes(rating)) + 
  stat_density(position = "identity", geom = "line", adjust = 3) + 
  facet_wrap(.~genres, strip.position = "bottom", nrow = 3) + theme_minimal() + 
  theme(axis.text.y = element_blank(), axis.title.y = element_blank(), axis.text.x = element_blank(),
        strip.text = element_text(family = "Ink Free", face = "bold", size = 20, colour = "firebrick4"), axis.title.x = element_blank())
```

---

```{r facet_example3, message = F, warning = F, fig.height=8, fig.width=16}
snails %>% ## snails dataset from the MASS library
  ggplot(aes(Exposure, Deaths, col = factor(Rel.Hum))) + 
  facet_grid(Species ~ Temp) + 
  geom_line() + 
  geom_point() + 
  theme_minimal() + 
  theme(legend.title = element_blank(), text = element_text(size = 20))
```

