---
title: "Themes (and fonts and scales)"
author: "Eugene"
date: "`r format(Sys.Date(), '%B %d %Y')`"
output:
  xaringan::moon_reader:
    css: [TUD01, TUD02, tamu-fonts]

header-includes:
- \usepackage{multicol}
- \newcommand{\btwocol}{\begin{multicols}{2}}
- \newcommand{\etwocol}{\end{multicols}}
---

class: center, inverse

# Using Themes in R
<br>

### We'll also discuss fonts (first) and scales.
- themes give fine control to the appearance of your plots
    - control over text size, fonts, text colour, etc
    - position of legends, titles, captions, etc
    - colours of backgrounds
    - delete unwanted features (like, say, tick marks on an axis)
    
---

class: center, inverse


- large number of preset themes
    - the _Wall Street Journal_ theme we used in assignment two
- several packages with neat bundle of useful themes
- and, of course, we can develop our own theme to have consistent graphics

---

## Fonts

- we'll discuss this first, as often themes require fonts which might not be present
- fonts are a whole world of their own
- see [practicaltypography.com](practicaltypography.com)

---

- need to be in the system, load them into windows / mac / linux
    - only really works for true type fonts (.ttf)
    - go to folder where the R library lives and seek out fonts
    - e.g. R/x86_64-pc/3.6/tvthemes/fonts/SpongeBob
    - click on .ttf files to install
- then need to capture them  in R
    - install package *extrafont*
    - run *ttf_import()* with path = folder from above
    - run *fonts()* to check available fonts
    - usually need to restart R (*Session* then *Restart R*)
- can also use google fonts, I load them through css, I'm sure there's a simpler way but I don't know it

---
## Complete Themes
- these set up ggplots with standard appearances
- can always adjust these, but do so in a layer after invoking the theme
- some defaults in ggplot2, see [here](https://ggplot2.tidyverse.org/reference/ggtheme.html)
- you should experiment with these to see how they look

```{r setup, echo = F, message=F, warning=F}
library(tidyverse)
library(scales)
library(gapminder)
```

---
.pull-left[

```{r themes1}
iris %>% ggplot(aes(Sepal.Length, Sepal.Width, col = Species)) + 
  geom_point() +
  theme_classic()
```

]
.pull-right[
```{r themes2}
iris %>% ggplot(aes(Sepal.Length, Sepal.Width, col = Species)) + 
  geom_point() +
  theme_dark()
```

]

---

## Complete Themes

- other package provide supplementary themes
    - *ggthemes*
    - *ggthemr* (see [here](https://github.com/cttobin/ggthemr))
    - *tvthemes* (see [here](https://ryo-n7.github.io/2019-05-16-introducing-tvthemes-package/))
    - *hrbrthemes* see [here](https://github.com/hrbrmstr/hrbrthemes)
    - *firatheme* (see [here](https://github.com/vankesteren/firatheme))
    - *bbplot*, themes from the BBC (see [here](https://github.com/bbc/bbplot))
    - *ggtech* themes from companies, e.g. Facebook. See [here](https://github.com/ricardo-bion/ggtech)
- [This website](https://rfortherestofus.com/2019/08/themes-to-improve-your-ggplot-figures/) is pretty good on themes
- again, make sure you experiment with these

---

## Fine Control Over Themes

- we can change any feature of a theme that we want
- type *?theme* on the console to see available themes
- use *element_&&&&&* to replace theme
- example: *theme(text = element_text(family = "Roboto Sans"))*

---


```{r themes3, fig.height=6}
iris %>% ggplot(aes(Sepal.Length, Sepal.Width, col = Species)) + 
  geom_point() +
  theme(text = element_text(family = "Ink Free", size = 20, face = "bold"))
```

---

```{r themes4, fig.height=6}
iris %>% ggplot(aes(Sepal.Length, Sepal.Width, col = Species)) + 
  geom_point() +
  theme(legend.position = "bottom", axis.text.y = element_blank())
```


---

```{r fig.height=4}
theme_bluewhite <- function (base_size = 11, base_family = "Get Schwifty") {
    theme_bw() %+replace% 
    theme( text = element_text(size = base_size, family = base_family),
      panel.grid.major  = element_line(color = "white"),
      panel.background = element_rect(fill = "lightblue"),
      panel.border = element_rect(color = "lightblue", fill = NA),
      axis.line = element_line(color = "lightblue"),
      axis.ticks = element_line(color = "lightblue"),
      axis.text = element_text(color = "steelblue")
      )
}
ggplot(ToothGrowth, aes(factor(dose), len)) + # Using our new theme
  geom_boxplot() +
  theme_bluewhite(base_size = 24)
```

---

class: center, inverse

# _scales_

- I like the scales package and feel it's worth discussing
- We used it to give dollar signs in the last assignment
- (also, has the _show_col()_ function)
- can be used to change to scientific notation, or not
- utilities like _comma()_, _dollar()_, _label_number_si()_, _percent()_, _pretty_breaks()_
- [this is a nice overview](https://bookdown.org/Maxine/ggplot2-maps/posts/2019-11-27-using-scales-package-to-modify-ggplot2-scale/)

---

```{r}
gapminder %>% ggplot(aes(gdpPercap, pop)) + 
  geom_point() + 
  scale_y_log10(label = label_number_si(unit = " people")) +
  scale_x_continuous(label = dollar) + theme(text = element_text(size = 20))
```


